Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/adversary.tex
move efficiency proof

\subsection{Efficiency}
\begin{lemma}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.
\end{lemma}
\begin{proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

%% From Lemma~\ref{lemma:tau1_increasing} 
% \[
% \tau_1(k, p_a, p_0, n_j) = 
%  \frac{P[K_r \geq {k} | H_a, n_j]}{P[K_r \geq {k} | H_0, n_j]}
% \]
%is a strictly increasing function of $k$ (for $0 < p_0, p_a < 1$ and $n_r > 0$). % for $k \geq k_r$. % (in fact this isk^{p_a, p_0, \alpha}_{min, \BRAVO, n_r} = k^{*}_{n_r}$
% \textit{i.e.,}
% \begin{equation}\label{eq_incr}
% % \frac{1}{\alpha} \leq
%   \frac{P[K_r = {k_r} | H_a, n_r]}{P[\mathbf{k_r} | H_0, n_r]} \leq   \frac{P[\mathbf{k_r} + 1 | H_a, n_r]}{P[K_r = {k_r} + 1 | H_0, n_r]} \leq \ldots  \leq \frac{P[\mathbf{n_r} | H_a, n_r]}{P[\mathbf{n_r} | H_0, n_r]}. 
% \end{equation}

%If the \BRAVO test is satisfied for $k_j$ then:

% From the properties of binomial distribution we obtain:
% \[
%    \frac{P[\mathbf{k_r} | H_a, n_r]}{P[\mathbf{k_r} | H_0, n_r]} = 
%    \frac{P[\mathbf{k_{r-1}} | H_a, n_{r-1}]}{P[\mathbf{k_{r-1}} | H_0, n_{r-1}]}
%    \frac{P[\mathbf{k_r - k_{r-1}} | H_a, n_r - n_{r-1}]}{P[\mathbf{k_r - k_{r-1}} | H_0, n_r - n_{r-1}]} = 
% \]
\[
 \frac{1}{\alpha} \leq \sigma(k_{j}, p_a, p_0, n_{j}) 
\]
\[
 = \sigma(k_{j-1}, p_a, p_0, n_{j-1}) \cdot \sigma(k_j - k_{j-1}, p_a, p_0, n_j - n_{j-1})  
\]
\[
 \leq^{(*)} \sigma(k_{j-1}, p_a, p_0, n_{j-1}) \cdot \tau_1(k_j - k_{j-1}, p_a, p_0, n_j - n_{j-1}) 
\]
\[
 = \omega_r(k_j, k_{j-1}, p_a, p_0, n_j, n_{j-1}).
\]

Where inequality $(*)$ follows from \cite[Theorem 6]{athena}. Note that we apply this result on $\tau_j$ for just $j=1$.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.

% 
% Now, if we consider $k^* = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ then it is easy to see that:
% 
% 
%  \[
%  k^{p_a, p_0, \alpha, k_{r-1}}_{min, [n_1, \ldots, n_r]}  
%   = \min\left\{k :
% \frac{
% s_{k_{r-1}, a, [n_{r-1}]}
% \sum_{i = k}^{n_r - n_{r-1}} s_{i, a, [n_r - n_{r-1}]}
% }{
% s_{k_{r-1}, 0, [n_{r-1}]}
% \sum_{i = k}^{n_r - n_{r-1}} s_{i, 0, [n_r - n_{r-1}]}
% }\geq \frac{1}{\alpha}  \right\} =
% \]
% \[
%   = \min\left\{k :
% \frac{
% s_{k_{r-1}, a, [n_{r-1}]}
% \left(
% \sum_{i = k}^{n_r - n_{r-1}} s_{i, a, [n_r - n_{r-1}]}
% + \sum_{i = k}^{n_r - n_{r-1}} s_{i, a, [n_r - n_{r-1}]}
% \right)
% }{
% s_{k_{r-1}, 0, [n_{r-1}]}
% \sum_{i = k}^{n_r - n_{r-1}} s_{i, 0, [n_r - n_{r-1}]}
% }\geq \frac{1}{\alpha}  \right\} =
% \]

%  \[
%  k^{p_a, p_0, \alpha}_{min, [n_1, \ldots, n_j]} =  k^{p_a, p_0, \alpha}_{min, [n_j]}
%         = \min\left\{k :
% \frac{
% \sum_{i = k}^{n_j} s_{i, a, [n_j]}
% }{
% \sum_{i = k}^{n_j} s_{i, 0, [n_j]}
% }\geq \frac{1}{\alpha}  \right\} =
% \]

% 
%  
%  Now, let us consider $j$-{th} round for $j = 1, \ldots, r$. We are going to show that
%  $k^{p_a, p_0, \alpha}_{min, [n_1, \ldots, n_j]} \leq k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$.
%  
%  From Lemma~\ref{eq:kMin} we have:
%  \[
%  k^{p_a, p_0, \alpha}_{min, [n_1, \ldots, n_j]} =  k^{p_a, p_0, \alpha}_{min, [n_j]}
%   = \min\left\{k :
% \frac{
% \sum_{i = k}^{n_j} s_{i, a, [n_j]}
% }{
% \sum_{i = k}^{n_j} s_{i, 0, [n_j]}
% }\geq \frac{1}{\alpha}  \right\} =
% \]
% 
% From the definition of $k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ we have that for every $k \geq k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ it holds: $s_{k, a, [n_j]}/s_{k, 0, [n_j]} \geq 1/\alpha$ which means that:
% \[
% \frac{
% \sum_{i = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}}^{n_j} s_{i, a, [n_j]}
% }{
% \sum_{i = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}}^{n_j} s_{i, 0, [n_j]}
% }\geq \frac{1}{\alpha}
% \]
% which means that $k^{p_a, p_0, \alpha}_{min, [n_1, \ldots, n_j]} \leq k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$.

\end{proof}

>>>>

\subsection{Efficiency}
\newtheorem{lem}{Lemma}
\begin{restatable}{lem}{efficiencylemma}
\label{lem:efficiency}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.
\end{restatable}
\begin{proof} Appendix~\ref{pf:efficiency_proof}\end{proof}

### 2022-10-12 providence/sections/appendix.tex
move efficiency proof

>>>>

\efficiencylemma

\begin{proof}
\label{pf:efficiency_proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

%% From Lemma~\ref{lemma:tau1_increasing} 
% \[
% \tau_1(k, p_a, p_0, n_j) = 
%  \frac{P[K_r \geq {k} | H_a, n_j]}{P[K_r \geq {k} | H_0, n_j]}
% \]
%is a strictly increasing function of $k$ (for $0 < p_0, p_a < 1$ and $n_r > 0$). % for $k \geq k_r$. % (in fact this isk^{p_a, p_0, \alpha}_{min, \BRAVO, n_r} = k^{*}_{n_r}$
% \textit{i.e.,}
% \begin{equation}\label{eq_incr}
% % \frac{1}{\alpha} \leq
%   \frac{P[K_r = {k_r} | H_a, n_r]}{P[\mathbf{k_r} | H_0, n_r]} \leq   \frac{P[\mathbf{k_r} + 1 | H_a, n_r]}{P[K_r = {k_r} + 1 | H_0, n_r]} \leq \ldots  \leq \frac{P[\mathbf{n_r} | H_a, n_r]}{P[\mathbf{n_r} | H_0, n_r]}. 
% \end{equation}

%If the \BRAVO test is satisfied for $k_j$ then:

% From the properties of binomial distribution we obtain:
% \[
%    \frac{P[\mathbf{k_r} | H_a, n_r]}{P[\mathbf{k_r} | H_0, n_r]} = 
%    \frac{P[\mathbf{k_{r-1}} | H_a, n_{r-1}]}{P[\mathbf{k_{r-1}} | H_0, n_{r-1}]}
%    \frac{P[\mathbf{k_r - k_{r-1}} | H_a, n_r - n_{r-1}]}{P[\mathbf{k_r - k_{r-1}} | H_0, n_r - n_{r-1}]} = 
% \]
\[
 \frac{1}{\alpha} \leq \sigma(k_{j}, p_a, p_0, n_{j}) 
\]
\[
 = \sigma(k_{j-1}, p_a, p_0, n_{j-1}) \cdot \sigma(k_j - k_{j-1}, p_a, p_0, n_j - n_{j-1})  
\]
\[
 \leq^{(*)} \sigma(k_{j-1}, p_a, p_0, n_{j-1}) \cdot \tau_1(k_j - k_{j-1}, p_a, p_0, n_j - n_{j-1}) 
\]
\[
 = \omega_r(k_j, k_{j-1}, p_a, p_0, n_j, n_{j-1}).
\]

Where inequality $(*)$ follows from \cite[Theorem 6]{athena}. Note that we apply this result on $\tau_j$ for just $j=1$.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.

% 
% Now, if we consider $k^* = k^{p_a, p_0, \alpha}_{min, \BRAVO, n_r}$ then it is easy to see that:
% 
% 
\end{proof}
